Moral Foundations of U.S. Political News Organizations

### 2019-03-19 pilot_manuscript.Rmd
new descriptive stats section
adding NYtimes GS

@@

```{r NYTimes, eval = F, include = F}

@@

>>>>

## Descriptive Statistics

overall valence for each source

types/tokens ratios, etc. for each source also number of articles

table - columns are types (unique words), tokens (total words), readability statistics, number of articles, total number of words, valence

## Inferential Statistics

@@

```{r NYTimes_kav, eval = F, include = F}

@@

```{r NYTimes_shut, eval = F, include = F}
library(rvest)
library(RSelenium)
library(beepr)

#page for NYTIMES
url <- 'https://www.nytimes.com/search?endDate=20190208&query=government%20shutdown&sort=best&startDate=20181208'

#with 803 results at 10 per page we need
#803 - 10 original / 10 per click is 80 clicks

for (i in 1:80) {
  webElem$clickElement()
  Sys.sleep(runif(1, 1, 5))
}

attr_data = html_attrs(headline_data) 
#attr_data

urlslist = unlist(attr_data)
urlslist = urlslist[grep(".html", urlslist)]
urlslist = urlslist[grep("/201", urlslist)]
urlslist = unique(urlslist)
urlslist

write.csv(NYtimesDF, "NYtimes_gs.csv", row.names = F)
beep(sound = 5)

remDr$close()
# stop the selenium server
rD[["server"]]$stop()
```
